Blocking-resistant communication through high-value web services

### 2014-05-13 docs/meek.tex
larger text size

\begin{abstract}
We describe meek, a blocking-resistant Internet communication system for censorship circumvention.
meek uses HTTP as a mechanism for transporting data, but it is not a steganographic HTTP transport;
rather, it relies on HTTPS to hide the contents of communications from a censor.
Communications are proxied through a web service that may itself be blocked by the censor:
``domain fronting''---in which the domain name used in the (censor-visible)
DNS request and TLS server name extension doesn't match the name in the (censor-invisible)
HTTP host header---enables communication that is apparently with an allowed host
but actually with a forbidden host.

Though HTTPS frustrates blocking by hiding the underlying communication,
differences in TLS implementations give rise to distinguishing features
that may be used to block circumvention traffic.
We describe how we use a web browser as a tool for making HTTPS requests,
so that the TLS signature of circumvention traffic resembles that of ordinary web browsing.
We present other, more subtle traffic characteristics that may enable blocking,
and identify potential countermeasures to such blocking.

We describe our experience implementing meek as a pluggable transport for Tor,
and the results of an initial experimental deployment.
\end{abstract}

@@

Traffic obfuscation has been approached in many different ways,
which may be classified into two general techniques.
The first technique is to look unlike
anything forbidden by the censor; that is, fail to match a blacklist. The second is
to resemble a protocol that is explicitly allowed by the censor; that is, match a whitelist.
Falling into the first category are ``look-like-nothing'' transports whose
payloads are indistinguishable from a uniformly random byte stream.
Classic example of look-like-nothing
protocols are obfs2~\cite{obfs2} and its successor obfs3~\cite{obfs3},
which have been Tor's go-to pluggable transports since early 2012~\cite{obfsproxy-arms-race}.
ScrambleSuit~\cite{scramblesuit} is like obfs3 in the
content of its payloads, but it takes additional steps to obscure its traffic signature
(packet lengths and timing), and is designed to resist active scanning for proxies
(the proxy server remains silent until the client proves knowledge of a shared
secret).

@@

>>>>

\begin{abstract}
We describe meek, a blocking-resistant Internet communication system for censorship circumvention.
A key technique we use is ``domain fronting''---communicating with
a forbidden domain name while appearing to communicate with one that is allowed.
\end{abstract}

@@

Traffic obfuscation has been approached in many different ways,
which may be classified into two general techniques.
The first technique is to look unlike
anything forbidden by the censor; that is, fail to match a blacklist. The second is
to resemble a protocol that is explicitly allowed by the censor; that is, match a whitelist.
Falling into the first category are ``look-like-nothing'' transports whose
payloads are indistinguishable from a uniformly random byte stream.
The classic example of a look-like-nothing
protocol is obfsproxy~\cite{obfsproxy}, long the go-to obfuscated
transport used by Tor. ScrambleSuit~\cite{scramblesuit} is like obfsproxy in the
content of its payloads, but it takes additional steps to obscure its traffic signature
(packet lengths and timing), and is designed to resist active scanning for proxies
(the proxy server remains silent until the client proves knowledge of a shared
secret).

@@

% 1. TCP payload length
% 2. Number of concurrent connections
% 3. Connection Lifetime

% Conclusion:
% 1. long-lived connections with bulk data transfer may be suspicious
% 2. Distribution of packet sizes
